---
title: "Take all the cells from the plan C clusters: 0, 2, 4, 5, 6, 8, 9, 13, 16, 17 (all these are PL) and perform sub-clustering."
author: "Yifang Liu"
date: "`r format(Sys.time(), tz='America/New_York', usetz=TRUE)`"
output:
  rmdformats::html_clean:
    code_folding: hide
    fig_width: 10
    fig_height: 10
    highlight: kate
    thumbnails: false
    lightbox: true
    gallery: true
---

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print = 200)
opts_chunk$set(echo = TRUE,
               cache = FALSE,
               prompt = FALSE,
               tidy = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE)
opts_knit$set(width = 75)
```

```{r setup}
# Specify seed for reproducibility
set.seed(123)

# Setup
library(Matrix)
library(tidyverse)
library(ggplot2)
library(Seurat)
library(cowplot)
library(Rcpp)
library(harmony)

npc <- 20
theta1 <- 2
theta2 <- 5
theta <- c(theta1, theta2)
pt_size <- 0.05
```

# Before Run Harmony

```{r initialize_seurat_object}
# Initialize Seurat Object
blood <- readRDS("data/cd_PL_cluster_191002.Rds")
rownames(blood) <- gsub('\\\\', '-', rownames(blood))
blood <- CreateSeuratObject(counts = blood, project = "blood", min.cells = 10, min.features = 100) %>%
    NormalizeData(verbose = FALSE) %>%
    FindVariableFeatures(selection.method = "vst", nfeatures = 2000) %>%
    ScaleData(features = rownames(blood), verbose = FALSE) %>%
    RunPCA(pc.genes = blood@var.genes, npcs = npc, verbose = FALSE)
```

```{r metadata}
blood[["percent.mito"]] <- PercentageFeatureSet(blood, pattern = "^mt:")

# Make sure that the dataset ID is in the object's metadata.
blood@meta.data$Sample <- c(
  rep("UNinjured", sum(
    sum(grepl("UNinjured_tenx_B1",colnames(blood))),
    sum(grepl("UNinjured_tenx_B3",colnames(blood))),
    sum(grepl("UNinjured_indrop_UC1",colnames(blood))),
    sum(grepl("UNinjured_indrop_UC2",colnames(blood)))
  )),
  rep("injured", sum(
    sum(grepl("injured_tenx_B2",colnames(blood))),
    sum(grepl("injured_tenx_B4",colnames(blood))),
    sum(grepl("injured_indrop_PC1",colnames(blood))),
    sum(grepl("injured_indrop_PC2",colnames(blood)))
  )),
  rep("WASP96hr", sum(
    sum(grepl("WASP96hr_dropseq_PI24CIRC1",colnames(blood))),
    sum(grepl("WASP96hr_dropseq_PI24CIRC2",colnames(blood))),
    sum(grepl("WASP96hr_dropseq_PI24CIRC3",colnames(blood)))
  ))
)

# Define order of appearance of timepoints
my_levels <- c("UNinjured", "injured", "WASP96hr")

# Relevel object@meta.data$Sample
blood@meta.data$Sample <- factor(x = blood@meta.data$Sample, levels = my_levels)

blood@meta.data$Technology <- c(
  rep("tenx", sum(
    sum(grepl("UNinjured_tenx_B1",colnames(blood))),
    sum(grepl("UNinjured_tenx_B3",colnames(blood)))
  )),
  rep("indrop", sum(
    sum(grepl("UNinjured_indrop_UC1",colnames(blood))),
    sum(grepl("UNinjured_indrop_UC2",colnames(blood)))
  )),
  rep("tenx", sum(
    sum(grepl("injured_tenx_B2",colnames(blood))),
    sum(grepl("injured_tenx_B4",colnames(blood)))
  )),
  rep("indrop", sum(
    sum(grepl("injured_indrop_PC1",colnames(blood))),
    sum(grepl("injured_indrop_PC2",colnames(blood)))
  )),
  rep("dropseq", sum(
    sum(grepl("WASP96hr_dropseq_PI24CIRC1",colnames(blood))),
    sum(grepl("WASP96hr_dropseq_PI24CIRC2",colnames(blood))),
    sum(grepl("WASP96hr_dropseq_PI24CIRC3",colnames(blood)))
  ))
)

# Define order of appearance of timepoints
my_levels <- c("tenx", "indrop", "dropseq")

# Relevel object@meta.data$Sample
blood@meta.data$Technology <- factor(x = blood@meta.data$Technology, levels = my_levels)

blood@meta.data$LibraryID <- c(
  rep("UNinjured_tenx_B1", sum(grepl("UNinjured_tenx_B1",colnames(blood)))),
  rep("UNinjured_tenx_B3", sum(grepl("UNinjured_tenx_B3",colnames(blood)))),
  rep("UNinjured_indrop_UC1", sum(grepl("UNinjured_indrop_UC1",colnames(blood)))),
  rep("UNinjured_indrop_UC2", sum(grepl("UNinjured_indrop_UC2",colnames(blood)))),
  rep("injured_tenx_B2", sum(grepl("injured_tenx_B2",colnames(blood)))),
  rep("injured_tenx_B4", sum(grepl("injured_tenx_B4",colnames(blood)))),
  rep("injured_indrop_PC1", sum(grepl("injured_indrop_PC1",colnames(blood)))),
  rep("injured_indrop_PC2", sum(grepl("injured_indrop_PC2",colnames(blood)))),
  rep("WASP96hr_dropseq_PI24CIRC1", sum(grepl("WASP96hr_dropseq_PI24CIRC1",colnames(blood)))),
  rep("WASP96hr_dropseq_PI24CIRC2", sum(grepl("WASP96hr_dropseq_PI24CIRC2",colnames(blood)))),
  rep("WASP96hr_dropseq_PI24CIRC3", sum(grepl("WASP96hr_dropseq_PI24CIRC3",colnames(blood))))
)

previous_cluster_info <- read.table("data/PL_cluster_metadata.txt", header = TRUE, stringsAsFactors = FALSE)
# identical(row.names(previous_cluster_info), row.names(blood@meta.data))
# all.equal(row.names(previous_cluster_info), row.names(blood@meta.data))

blood@meta.data$previous_cluster_info <- previous_cluster_info$merge_cluster %>% as.factor()
```

There is a clear difference between the technology in the uncorrected PCs

```{r difference_pc}
p1 <- DimPlot(object = blood, reduction = "pca", group.by = "Sample", do.return = TRUE, pt.size = pt_size)
p2 <- VlnPlot(object = blood, features = "PC_1", group.by = "Sample", do.return = TRUE, pt.size = pt_size)
p3 <- DimPlot(object = blood, reduction = "pca", group.by = "Technology", do.return = TRUE, pt.size = pt_size)
p4 <- VlnPlot(object = blood, features = "PC_1", group.by = "Technology", do.return = TRUE, pt.size = pt_size)

plot_grid(p1, p2, p3, p4)
```

# After Run Harmony

```{r run_harmony}
blood <- blood %>%
  RunHarmony(c("Sample", "Technology"), theta = theta, plot_convergence = FALSE, max.iter.harmony = 20)
```

The datasets are well integrated in the first 2 dimensions after Harmony.

```{r harmony_pc}
p1 <- DimPlot(object = blood, reduction = "harmony", group.by = "Sample", do.return = TRUE, pt.size = pt_size)
p2 <- VlnPlot(object = blood, features = "harmony_1", group.by = "Sample", do.return = TRUE, pt.size = pt_size)
p3 <- DimPlot(object = blood, reduction = "harmony", group.by = "Technology", do.return = TRUE, pt.size = pt_size)
p4 <- VlnPlot(object = blood, features = "harmony_1", group.by = "Technology", do.return = TRUE, pt.size = pt_size)

plot_grid(p1, p2, p3, p4)
```

# Downstream Analysis

```{r downstream_analysis}
blood <- blood %>%
  RunUMAP(reduction = "harmony", dims = 1:npc) %>%
  RunTSNE(reduction = "harmony", dims = 1:npc) %>%
  FindNeighbors(reduction = "harmony", dims = 1:npc, verbose = FALSE, force.recalc = TRUE) %>%
  FindClusters(resolution = seq(0.1, 1, 0.1), verbose = FALSE) %>%
  identity()
```

# Sample / Technology / LibraryID / Percent mito / Previous cluster info - UMAP {.tabset}

## Sample

```{r sample_umap}
DimPlot(blood, reduction = "umap", group.by = "Sample", pt.size = pt_size)
```

## Technology

```{r technology_umap}
DimPlot(blood, reduction = "umap", group.by = "Technology", pt.size = pt_size)
```

## LibraryID

```{r libraryid_umap}
DimPlot(blood, reduction = "umap", group.by = "LibraryID", pt.size = pt_size)
```

## Percent mito

```{r percent_mito_umap}
FeaturePlot(blood, reduction = "umap", features = c("percent.mito"), pt.size = pt_size)
```

## Previous cluster info

```{r Previous_cluster_info_umap}
DimPlot(blood, reduction = "umap", group.by = "previous_cluster_info", pt.size = pt_size)
```


# UMAP - resolutions {.tabset}

In the UMAP embedding, we can see more intricate structure. Since we used harmony embeddings, the UMAP embeddings are well mixed.

```{r UMAP_resolutions, results = 'asis'}
for(res in seq(0.1, 1, 0.1)){
  cat("\n")
  cat("\n##", "Cluster resolution: ", res, "{.tabset}\n")
  selected_res <- paste0("RNA_snn_res.", res)
  Idents(blood) <- selected_res
  p <- DimPlot(blood, reduction = "umap", label = TRUE, pt.size = pt_size)
  print(p)
  cat("\n")
}
```

# UMAP - Resolutions - Split {.tabset}

In the UMAP embedding, we can see more intricate structure. Since we used harmony embeddings, the UMAP embeddings are well mixed.

```{r umap_resolutions_split, results = 'asis'}
for(res in seq(0.1, 1, 0.1)){
  cat("\n")
  cat("\n##", "Cluster resolution: ", res, "{.tabset}\n")
  selected_res <- paste0("RNA_snn_res.", res)
  Idents(blood) <- selected_res
  p <- DimPlot(blood, reduction = "umap", label = TRUE, split.by = "Sample", pt.size = pt_size)
  print(p)
  cat("\n")
}
```

# Sample / Technology / LibraryID / Percent mito / Previous cluster info - TSNE {.tabset}

## Sample

```{r sample_tsne}
DimPlot(blood, reduction = "tsne", group.by = "Sample", pt.size = pt_size)
```

## Technology

```{r technology_tsne}
DimPlot(blood, reduction = "tsne", group.by = "Technology", pt.size = pt_size)
```

## LibraryID

```{r libraryid_tsne}
DimPlot(blood, reduction = "tsne", group.by = "LibraryID", pt.size = pt_size)
```

## Percent mito

```{r percent_mito_tsne}
FeaturePlot(blood, reduction = "tsne", features = c("percent.mito"), pt.size = pt_size)
```

## Previous cluster info

```{r Previous_cluster_info_tsne}
DimPlot(blood, reduction = "umap", group.by = "previous_cluster_info", pt.size = pt_size)
```

# TSNE - resolutions {.tabset}

```{r tsne_resolutions, results = 'asis'}
for(res in seq(0.1, 1, 0.1)){
  cat("\n")
  cat("\n##", "Cluster resolution: ", res, "{.tabset}\n")
  selected_res <- paste0("RNA_snn_res.", res)
  Idents(blood) <- selected_res
  p <- DimPlot(blood, reduction = "tsne", label = TRUE, pt.size = pt_size)
  print(p)
  cat("\n")
}
```

# TSNE - Resolutions - Split {.tabset}

```{r tsne_resolutions_split, results = 'asis'}
for(res in seq(0.1, 1, 0.1)){
  cat("\n")
  cat("\n##", "Cluster resolution: ", res, "{.tabset}\n")
  selected_res <- paste0("RNA_snn_res.", res)
  Idents(blood) <- selected_res
  p <- DimPlot(blood, reduction = "tsne", label = TRUE, split.by = "Sample", pt.size = pt_size)
  print(p)
  cat("\n")
}
```

# Markers

```{r markers}
selected_genes <- read.table("data/Markers.txt", header = TRUE)
DT::datatable(selected_genes)
```

## UMAP {.tabset}

```{r markers_umap, results = "asis"}
selected_genes <- selected_genes %>% dplyr::filter(geneName %in% rownames(blood))
selected_genes <- selected_genes[rowSums(as.matrix(GetAssayData(blood)[selected_genes$geneName, ])) > 0, ]
plot_feature_plot_wrapper <- function(obj, sub_df){
  p <- FeaturePlot(obj, features = sub_df[3], cols = c("grey", "blue"),
                   reduction = "umap", pt.size = pt_size)
  return(p)
}
for(cell_t in unique(selected_genes$cellType)){
  cat("\n")
  cat("###", cell_t, " {.tabset} \n")
  df <- selected_genes %>% dplyr::filter(cellType == cell_t)
  df_split <- split(df, ceiling(seq_along(df$geneName)/2))
  for(i in names(df_split)){
    cat("\n")
    cat("####", paste(cell_t, i, sep = "-"), "\n")
    plot_list <- apply(df_split[[i]], 1, FUN = function(x){plot_feature_plot_wrapper(blood, x)})
    p_l <- plot_grid(plotlist = plot_list, ncol = 1)
    print(p_l)
    cat("\n")
  }
  cat("\n")
}
```

## UMAP - Split {.tabset}

```{r markers_umap_split, results = "asis"}
selected_genes <- selected_genes %>% dplyr::filter(geneName %in% rownames(blood))
selected_genes <- selected_genes[rowSums(as.matrix(GetAssayData(blood)[selected_genes$geneName,])) > 0, ]
plot_feature_plot_wrapper <- function(obj, sub_df){
  p <- FeaturePlot(obj, features = sub_df[3], cols = c("grey", "blue"),
                   reduction = "umap",  split.by = "Sample", pt.size = pt_size)
  return(p)
}
for(cell_t in unique(selected_genes$cellType)){
  cat("\n")
  cat("###", cell_t," {.tabset} \n")
  df <- selected_genes %>% dplyr::filter(cellType == cell_t)
  df_split <- split(df, ceiling(seq_along(df$geneName)/2))
  for(i in names(df_split)){
    cat("\n")
    cat("####", paste(cell_t, i, sep = "-"), "\n")
    plot_list <- apply(df_split[[i]], 1, FUN = function(x){plot_feature_plot_wrapper(blood, x)})
    p_l <- plot_grid(plotlist = plot_list, ncol = 1)
    print(p_l)
    cat("\n")
  }
  cat("\n")
}
```

## TSNE {.tabset}

```{r markers_tsne, results = "asis"}
selected_genes <- selected_genes %>% dplyr::filter(geneName %in% rownames(blood))
selected_genes <- selected_genes[rowSums(as.matrix(GetAssayData(blood)[selected_genes$geneName,])) > 0, ]
plot_feature_plot_wrapper <- function(obj,sub_df){
  p <- FeaturePlot(obj, features = sub_df[3], cols = c("grey", "blue"),
                   reduction = "tsne", pt.size = pt_size)
  return(p)
}

for(cell_t in unique(selected_genes$cellType)){
  cat("\n")
  cat("###", cell_t," {.tabset} \n")
  df <- selected_genes %>% dplyr::filter(cellType == cell_t)
  df_split <- split(df, ceiling(seq_along(df$geneName)/2))
  for(i in names(df_split)){
    cat("\n")
    cat("####", paste(cell_t, i, sep = "-"), "\n")
    plot_list <- apply(df_split[[i]], 1, FUN = function(x){plot_feature_plot_wrapper(blood, x)})
    p_l <- plot_grid(plotlist = plot_list, ncol = 1)
    print(p_l)
    cat("\n")
  }
  cat("\n")
}
```

## TSNE - Split {.tabset}

```{r markers_tsne_split, results = "asis"}
selected_genes <- selected_genes %>% dplyr::filter(geneName %in% rownames(blood))
selected_genes <- selected_genes[rowSums(as.matrix(GetAssayData(blood)[selected_genes$geneName,])) > 0, ]
plot_feature_plot_wrapper <- function(obj, sub_df){
  p <- FeaturePlot(obj, features = sub_df[3], cols = c("grey", "blue"),
                   reduction = "tsne",  split.by = "Sample", pt.size = pt_size)
  return(p)
}

for(cell_t in unique(selected_genes$cellType)){
  cat("\n")
  cat("###", cell_t," {.tabset} \n")
  df <- selected_genes %>% dplyr::filter(cellType == cell_t)
  df_split <- split(df, ceiling(seq_along(df$geneName)/2))
  for(i in names(df_split)){
    cat("\n")
    cat("####", paste(cell_t, i, sep = "-"), "\n")
    plot_list <- apply(df_split[[i]], 1, FUN = function(x){plot_feature_plot_wrapper(blood, x)})
    p_l <- plot_grid(plotlist = plot_list, ncol = 1)
    print(p_l)
    cat("\n")
  }
  cat("\n")
}
```

```{r save_Rds}
saveRDS(blood, file = "output/Plasmatocyte_sub_clustering_resolution_0.4_npc_20_theta_2_5_191002.Rds")
```

# Clusters resolution = 0.4

```{r resolution}
DefaultAssay(blood) <- "RNA"
resolution <- 0.4
selected_res <- paste0("RNA_snn_res.", resolution)
Idents(blood) <- selected_res
```


```{r findMarkers}
if (file.exists(paste0("output/findMarkers_", "resolution_", resolution, "_npc_", npc, "_theta_", theta1, "_", theta2, ".Rds"))) {
    markers_list <- readRDS(paste0("output/findMarkers_", "resolution_", resolution, "_npc_", npc, "_theta_", theta1, "_", theta2, ".Rds"))
}else{
  table_df <- table(blood@meta.data[ , selected_res], blood@meta.data$Sample) %>%
    as.data.frame() %>% spread(key = Var2, value =Freq)
  colnames(table_df)[1] <- "cluster"
  markers_list <- list()
  for(cluster_id in table_df$cluster){
      markers <- FindMarkers(blood, ident.1 = cluster_id)
      markers$gene_name <- row.names(markers)
      write.csv(markers, file = paste0("output/findMarkers_", "resolution_", resolution, "_npc_", npc, "_theta_", theta1, "_", theta2, "_cluster_", cluster_id, ".csv"))
      markers_list[[paste0("cluster_", cluster_id)]] <- markers
  }
  saveRDS(markers_list,
          file = paste0("output/findMarkers_", "resolution_", resolution, "_npc_", npc, "_theta_", theta1, "_", theta2, ".Rds"))
}
```

## Clusters - UMAP {.tabset}

```{r plot_marker_genes_clusters_umap, results = "asis"}
plot_feature_plot_wrapper <- function(obj, sub_df){
  # print(sub_df["gene_name"])
    p <- FeaturePlot(obj, features = sub_df["gene_name"], cols = c("grey", "blue"),
reduction = "umap", pt.size = pt_size)
    return(p)
}

for(cluster_n in names(markers_list)){
    cat("\n")
    cat("### ", cluster_n," {.tabset} \n")
    # df <- markers_list[[`cluster_n`]][1:min(12,dim(markers_list[[`cluster_n`]])[1]),]
    df <- markers_list[[`cluster_n`]]
    # df <- df[order(df$avg_logFC, decreasing = TRUE), ]
    df <- subset(df, df$avg_logFC > 0)
    df <- df[1:20,]
    df_split <- split(df, ceiling(seq_along(df$gene_name)/4))
    for(i in names(df_split)){
        cat("\n")
        cat("####", paste(cluster_n, i, sep = "-"), "\n")
        plot_list <- apply(df_split[[i]],1,FUN = function(x){plot_feature_plot_wrapper(blood, x)})
        p_l <- plot_grid(plotlist = plot_list, ncol = 2)
        print(p_l)
        cat("\n")
    }
    cat("\n")
}
```

## Clusters - UMAP - Split {.tabset}

```{r plot_marker_genes_clusters_umap_split, results = "asis"}
plot_feature_plot_wrapper <- function(obj, sub_df){
  # print(sub_df["gene_name"])
    p <- FeaturePlot(obj, features = sub_df["gene_name"], cols = c("grey", "blue"),
reduction = "umap", split.by = "Sample", pt.size = pt_size)
    return(p)
}

for(cluster_n in names(markers_list)){
    cat("\n")
    cat("### ", cluster_n, " {.tabset} \n")
    # df <- markers_list[[`cluster_n`]][1:min(12,dim(markers_list[[`cluster_n`]])[1]),]
    df <- markers_list[[`cluster_n`]]
    # df <- df[order(df$avg_logFC, decreasing = TRUE), ]
    df <- subset(df, df$avg_logFC > 0)
    df <- df[1:20,]
    df_split <- split(df, ceiling(seq_along(df$gene_name)/2))
    for(i in names(df_split)){
        cat("\n")
        cat("####", paste(cluster_n, i, sep = "-"), "\n")
        plot_list <- apply(df_split[[i]],1,FUN = function(x){plot_feature_plot_wrapper(blood, x)})
        p_l <- plot_grid(plotlist = plot_list, ncol = 1)
        print(p_l)
        cat("\n")
    }
    cat("\n")
}
```

## Clusters - t-SNE {.tabset}

```{r plot_marker_genes_clusters_tsne, results = "asis"}
plot_feature_plot_wrapper <- function(obj, sub_df){
  # print(sub_df["gene_name"])
    p <- FeaturePlot(obj, features = sub_df["gene_name"], cols = c("grey", "blue"),
reduction = "tsne", pt.size = pt_size)
    return(p)
}

for(cluster_n in names(markers_list)){
    cat("\n")
    cat("### ", cluster_n," {.tabset} \n")
    # df <- markers_list[[`cluster_n`]][1:min(12,dim(markers_list[[`cluster_n`]])[1]),]
    df <- markers_list[[`cluster_n`]]
    # df <- df[order(df$avg_logFC, decreasing = TRUE), ]
    df <- subset(df, df$avg_logFC > 0)
    df <- df[1:20,]
    df_split <- split(df, ceiling(seq_along(df$gene_name)/4))
    for(i in names(df_split)){
        cat("\n")
        cat("####", paste(cluster_n, i, sep = "-"), "\n")
        plot_list <- apply(df_split[[i]],1,FUN = function(x){plot_feature_plot_wrapper(blood, x)})
        p_l <- plot_grid(plotlist = plot_list, ncol = 2)
        print(p_l)
        cat("\n")
    }
    cat("\n")
}
```

## Clusters - t-SNE - Split {.tabset}

```{r plot_marker_genes_clusters_tsne_split, results = "asis"}
plot_feature_plot_wrapper <- function(obj, sub_df){
  # print(sub_df["gene_name"])
    p <- FeaturePlot(obj, features = sub_df["gene_name"], cols = c("grey", "blue"),
reduction = "tsne", split.by = "Sample", pt.size = pt_size)
    return(p)
}

for(cluster_n in names(markers_list)){
    cat("\n")
    cat("### ", cluster_n," {.tabset} \n")
    # df <- markers_list[[`cluster_n`]][1:min(12,dim(markers_list[[`cluster_n`]])[1]),]
    df <- markers_list[[`cluster_n`]]
    # df <- df[order(df$avg_logFC, decreasing = TRUE), ]
    df <- subset(df, df$avg_logFC > 0)
    df <- df[1:20,]
    df_split <- split(df, ceiling(seq_along(df$gene_name)/2))
    for(i in names(df_split)){
        cat("\n")
        cat("####", paste(cluster_n, i, sep = "-"), "\n")
        plot_list <- apply(df_split[[i]],1,FUN = function(x){plot_feature_plot_wrapper(blood, x)})
        p_l <- plot_grid(plotlist = plot_list, ncol = 1)
        print(p_l)
        cat("\n")
    }
    cat("\n")
}
```

## Clusters - Violin {.tabset}

```{r plot_marker_genes_clusters_violin, results = "asis"}
for(cluster_n in names(markers_list)){
    cat("\n")
    cat("### ", cluster_n," {.tabset} \n")
    df <- markers_list[[`cluster_n`]]
    # df <- df[order(df$avg_logFC, decreasing = TRUE), ]
    df <- subset(df, df$avg_logFC > 0)
    df <- df[1:20, ]
    # df <- markers_list[[`cluster_n`]][1:6,]
    df_split <- split(df, ceiling(seq_along(df$gene_name)/1))
    for(i in names(df_split)){
    cat("\n")
    cat("####", paste(cluster_n,i,sep="-"), "\n")
    plot <- VlnPlot(blood, features =  df_split[[i]]$gene_name,  group.by = selected_res,
    pt.size = 0, combine = FALSE)
    p <- plot[[1]] + ggtitle(df_split[[i]]$gene_name)
    print(p)
    cat("\n")
    }
    cat("\n")
}
```

## Clusters - Violin - Split {.tabset}

```{r plot_marker_genes_clusters_violin_split, results = "asis"}
for(cluster_n in names(markers_list)){
    cat("\n")
    cat("### ", cluster_n, " {.tabset} \n")
    df <- markers_list[[`cluster_n`]]
    # df <- df[order(df$avg_logFC, decreasing = TRUE), ]
    df <- subset(df, df$avg_logFC > 0)
    df <- df[1:20, ]
    df_split <- split(df, ceiling(seq_along(df$gene_name)/1))
    for(i in names(df_split)){
    cat("\n")
    cat("####", paste(cluster_n,i,sep="-"),"\n")
    plot <- VlnPlot(blood, features =  df_split[[i]]$gene_name,  group.by = selected_res,
    pt.size = 0, combine = FALSE, split.by = "Sample")
    p <- plot[[1]] + ggtitle(df_split[[i]]$gene_name)
    print(p)
    cat("\n")
    }
    cat("\n")
}
```

## Clusters - Dotplot - All Cluster {.tabset}

```{r DotPlot_allcluster, results = "asis"}
for (n in c(1:20)) {
  cat("\n")
  cat("### ", paste0("Top ", n, " markers each"), " {.tabset} \n")
  gene_list <- character(length = 0)
  for(cluster_n in names(markers_list)){
    df <- markers_list[[`cluster_n`]]
    df <- subset(df, df$avg_logFC > 0)
    count <- 0
    gene_names <- df$gene_name
    for (i in 1:length(gene_names)) {
      if (gene_names[i] %in% gene_list) {
        # print(cluster_n)
        # print(i)
        # print(gene_names[i])
      } else {
        gene_list <- c(gene_names[i], gene_list)
        count <- count + 1
      }
      if (count == n) {
        break
      }
    }
  }
  p <- DotPlot(blood, features = gene_list,  group.by = selected_res, dot.scale = 5.2) + RotatedAxis() + ylab("Cluster") + theme(axis.text.x = element_text(size = 11))
  print(p)
  cat("\n")
}
```

## Clusters - Dotplot - Split {.tabset}

```{r DotPlot_split, results = "asis"}
for (n in c(1:20)) {
  cat("\n")
  cat("### ", paste0("Top ", n, " markers each"), " {.tabset} \n")
  gene_list <- character(length = 0)
  for(cluster_n in names(markers_list)){
    df <- markers_list[[`cluster_n`]]
    df <- subset(df, df$avg_logFC > 0)
    count <- 0
    gene_names <- df$gene_name
    for (i in 1:length(gene_names)) {
      if (gene_names[i] %in% gene_list) {
        # print(cluster_n)
        # print(i)
        # print(gene_names[i])
      } else {
        gene_list <- c(gene_names[i], gene_list)
        count <- count + 1
      }
      if (count == n) {
        break
      }
    }
  }
  p <- DotPlot(blood, features = gene_list, group.by = selected_res, dot.scale = 4.3, split.by = "Sample", cols = c("#F25122", "#02A4EF", "#FFBA02")) +
    RotatedAxis() + ylab("Cluster") + theme(axis.text.x = element_text(size = 10))
  print(p)
  cat("\n")
}
```

## Clusters - Heatmap {.tabset}

```{r clusters_heatmap, results = "asis"}
for (n in c(3, 5, 10)) {
  cat("\n")
  cat("### ", paste0("Top ", n, " marker genes in each cluster"), " {.tabset} \n")
  gene_list <- character(length = 0)
  for(cluster_n in names(markers_list)){
    df <- markers_list[[`cluster_n`]]
    df <- subset(df, df$avg_logFC > 0)
    count <- 0
    gene_names <- df$gene_name
    for (i in 1:length(gene_names)) {
      if (gene_names[i] %in% gene_list) {
        # print(cluster_n)
        # print(i)
        # print(gene_names[i])
      } else {
        gene_list <- c(gene_names[i], gene_list)
        count <- count + 1
      }
      if (count == n) {
        break
      }
    }
  }
  p <- DoHeatmap(blood, features = gene_list)
  print(p)
  cat("\n")
}
```

## Clusters - Heatmap - Downsample300 {.tabset}

Downsample the clusters to a maximum of 300 cells each (makes the heatmap easier to see for small clusters)

```{r clusters_heatmap_Downsample300, results = "asis"}
for (n in c(3, 5, 10)) {
  cat("\n")
  cat("##", paste0("Top ", n, " marker genes in each cluster"), " {.tabset} \n")
  gene_list <- character(length = 0)
  for(cluster_n in names(markers_list)){
    df <- markers_list[[`cluster_n`]]
    df <- subset(df, df$avg_logFC > 0)
    count <- 0
    gene_names <- df$gene_name
    for (i in 1:length(gene_names)) {
      if (gene_names[i] %in% gene_list) {
        # print(cluster_n)
        # print(i)
        # print(gene_names[i])
      } else {
        gene_list <- c(gene_names[i], gene_list)
        count <- count + 1
      }
      if (count == n) {
        break
      }
    }
  }
  p <- DoHeatmap(subset(blood, downsample = 300), features = gene_list)
  print(p)
  cat("\n")
}
```

# Notes

Wed Oct 2, 2019:

  * Take all the cells from the plan C clusters: 0, 2, 4, 5, 6, 8, 9, 13, 16, 17 (all these are PL) and perform sub-clustering.

Wed Sep 11, 2019:

  * planC: merge cluster 0, 1, 14, 19 into 0.

Tuesday, August 27, 2019:

  * If a marker is already appeared in previous cluster, the follow up marker will be added, so that every cluster will have the same number of markers.

Monday, August 26, 2019:

  * Add marker genes, dotplot, heatmap.

Sunday, August 25, 2019:

  * If a gene express two out of three samples, we will keep these genes.

Monday, August 22, 2019:

  * Add Heatmap.

Monday, August 19, 2019:

  * Add find markers, Dotplot.

Friday, August 9, 2019:

  * Integrate analysis of UNinjured, injured and WASP96hr data, add Markers combined map.

Friday, August 2, 2019:

  * Split sample to different libraries, add QC, add combined map, change resolution (0.1 to 1).

Thursday, August 1, 2019:

  * Select the list of all cells of the 2 clusters (cluster 6 and 10) and do a clustering to see the sub-clusters.

Monday, July 29, 2019:

  * First version for integrate analysis of UNinjured injured WASP 10x indrop dropseq data.

# Session Info

```{r sessioninfo, message=TRUE}
sessionInfo()
```
