---
title: "uninjured_injured_integration - Separated samples - Harmony"
author: "Victor Barrera"
date: ""
output: html_document
params:
    outputDir: "."
    integrated_file: "./results/2019-07-25/intersect/all_data.Rda"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE ,warning = FALSE}
# Shared R Markdown settings
if (file.exists("_setup.R")) {
    source("_setup.R")
}
```

```{r}
# Specify seed for reproducibility
set.seed(1234567890)
```

```{r check-library-functions, echo=FALSE, message=FALSE}
'%!in%' <- function(x,y)!('%in%'(x,y))


# function to check installed libraries
check_install = function(packages) {
    not_installed = setdiff(packages, rownames(installed.packages()))
    if (length(not_installed) > 0) {
        write(paste("The libraries", not_installed, "are not installed, aborting.",
                    sep = " "), stderr())
        stop()
    }
}
```

```{r load-libraries, echo=FALSE, message=FALSE, warning=FALSE}
# load requiered library after checking if installed
packages = c("Seurat", "reticulate","AnnotationHub","ggplot2","cowplot", "dplyr", "harmony")
check_install(packages)
installed = lapply(packages, library, character.only = TRUE)
```

```{r}
# load conda environment that contains umap-learning for umap plots
use_condaenv("bioPython", conda = "/Users/victorbarrera/software/miniconda2/bin/conda", required = TRUE)
```

```{r}
ah <- AnnotationHub()
ahDb <- query(ah, pattern = c("Drosophila Melanogaster","EnsDb") )

id <- ahDb %>% 
     mcols() %>%  
        rownames() %>%
        tail(n = 1)

## Download the appropriate Ensembldb database
ahEnsdb <- ahDb[[id]]

rows <- genes(ahEnsdb)  %>% 
    as.data.frame() %>% 
    dplyr::mutate(gene_name = toupper(gene_name)) %>% 
    dplyr::select(c(gene_id,gene_name))
```

```{r}
ann_genes <- function(df, ann_df){
    df <- df %>% tibble::rownames_to_column(var = "gene_id")
    colnames(ann_df) <- c("gene_id","gene_name")
    joined_df <- dplyr::left_join(df, ann_df, by = "gene_id")
    joined_df <- joined_df %>% dplyr::mutate(gene_name = ifelse(is.na(gene_name),gene_id,gene_name)) 
    return(invisible(joined_df))
}
```

```{r, load-data}
load(params$integrated_file)
```

```{r}
options(repr.plot.height = 5, repr.plot.width = 12)
p1 <- DimPlot(object = all_data, reduction = "pca", pt.size = .1, group.by = "injured_st", do.return = TRUE)
p2 <- VlnPlot(object = all_data, features = "PC_1", group.by = "injured_st", do.return = TRUE, pt.size = .1)
plot_grid(p1,p2)
```

```{r}
options(repr.plot.height = 5, repr.plot.width = 12)
p1 <- DimPlot(object = all_data, reduction = "pca", pt.size = .1, group.by = "tech", do.return = TRUE)
p2 <- VlnPlot(object = all_data, features = "PC_1", group.by = "tech", do.return = TRUE, pt.size = .1)
plot_grid(p1,p2)
```

```{r, eval = FALSE}
all_data <- JackStraw(all_data, reduction = "pca", dims = 30)
```

```{r, eval = FALSE}
all_data <- ScoreJackStraw(all_data, dims = 1:30)
```


``````{r, eval = FALSE}
JackStrawPlot(all_data, dims = 1:30)
```

```{r, eval = FALSE}
ElbowPlot(all_data, ndims = 30)
```

```{r}
options(repr.plot.height = 5, repr.plot.width = 12)
p1 <- DimPlot(object = all_data, reduction = "harmony", pt.size = .1, group.by = "injured_st", do.return = TRUE)
p2 <- DimPlot(object = all_data, reduction = "harmony", pt.size = .1, group.by = "tech", do.return = TRUE)
p3 <- VlnPlot(object = all_data, features = "harmony_1", group.by = "injured_st", do.return = TRUE, pt.size = .1)
p4 <- VlnPlot(object = all_data, features = "harmony_1", group.by = "tech", do.return = TRUE, pt.size = .1)

plot_grid(p1,p2,p3,p4)
```





# UMAP - resolutions {.tabset}

```{r, results = 'asis'}
options(repr.plot.height = 4, repr.plot.width = 6)
for(res in seq(0.1,2,0.1)){
  cat("\n")
  cat("\n##","Cluster resolution: ",res,"{.tabset}\n")
  selected_res = paste0( "RNA_snn_res.",res)
  Idents(all_data) <- selected_res
  p <- DimPlot(all_data, reduction = "umap", label = TRUE, pt.size = .1, split.by = "injured_st")
  print(p)
  cat("\n")
}
```

# Injury/Tech/mito - UMAP{.tabset}

## injured_st

```{r}
options(repr.plot.height = 4, repr.plot.width = 6)
DimPlot(all_data, reduction = "umap", pt.size = .1, group.by = "injured_st")
```

## tech

```{r}
options(repr.plot.height = 4, repr.plot.width = 10)
DimPlot(all_data, reduction = "umap", group.by = "tech", pt.size = .1)
```

## percent mito

```{r}
options(repr.plot.height = 4, repr.plot.width = 10)
FeaturePlot(all_data, reduction = "umap", features = c("percent.mito"), pt.size = .1)
```


# TSNE - resolutions {.tabset}

```{r, results = 'asis'}
options(repr.plot.height = 4, repr.plot.width = 6)
for(res in seq(0.1,2,0.1)){
  cat("\n")
  cat("\n##","Cluster resolution: ",res,"{.tabset}\n")
  selected_res = paste0( "RNA_snn_res.",res)
  Idents(all_data) <- selected_res
  p <- DimPlot(all_data, reduction = "tsne", label = TRUE, pt.size = .1, split.by = "injured_st")
  print(p)
  cat("\n")
}
```

# Injury/Tech/mito - TSNE {.tabset}

## injured_st

```{r}
options(repr.plot.height = 4, repr.plot.width = 6)
DimPlot(all_data, reduction = "tsne", pt.size = .1, group.by = "injured_st")
```

## tech

```{r}
options(repr.plot.height = 4, repr.plot.width = 10)
DimPlot(all_data, reduction = "tsne", group.by = "tech", pt.size = .1)
```

## percent mito

```{r}
options(repr.plot.height = 4, repr.plot.width = 10)
FeaturePlot(all_data, reduction = "tsne", features = c("percent.mito"), pt.size = .1)
```


# Markers 

```{r}
selected_genes <- rio::import("./markers.csv")
```

Genes:

```{r}
DT::datatable(selected_genes)
```


## UMAP{.tabset}

```{r, results = "asis"}
selected_genes <- selected_genes %>% dplyr::filter(geneID %in% rownames(all_data))


selected_genes <- selected_genes[rowSums(as.matrix(GetAssayData(all_data)[selected_genes$geneID,]))>0,]

plot_feature_plot_wrapper <- function(obj,sub_df){
    p <- FeaturePlot(obj, features = sub_df[2],cols = c("grey", "blue"), 
reduction = "umap",min.cutoff = 1,  split.by = "injured_st")
    if(is.na(sub_df[3])){
       p <- p + ggtitle(sub_df[2]) %>% invisible()
    }else{
       p <- p + ggtitle(sub_df[3]) %>% invisible()
    }
    return(p)
}

for(cell_t in unique(selected_genes$cellType)){
    cat("\n")
    cat("###",cell_t," {.tabset} \n")
    df <- selected_genes %>% dplyr::filter(cellType == cell_t)
    df_split <- split(df, ceiling(seq_along(df$geneID)/4))
    for(i in names(df_split)){
        cat("\n")
        cat("####",paste(cell_t,i,sep="-"),"\n")
        
        plot_list <- apply(df_split[[i]],1,FUN = function(x){plot_feature_plot_wrapper(all_data,x)})
        
        
        p_l <- plot_grid(plotlist = plot_list,ncol = 2)
        print(p_l)
        cat("\n")
    }
    cat("\n")
}

```



## TSNE{.tabset}

```{r, results = "asis"}
selected_genes <- selected_genes %>% dplyr::filter(geneID %in% rownames(all_data))


selected_genes <- selected_genes[rowSums(as.matrix(GetAssayData(all_data)[selected_genes$geneID,]))>0,]

plot_feature_plot_wrapper <- function(obj,sub_df){
    p <- FeaturePlot(obj, features = sub_df[2],cols = c("grey", "blue"), 
reduction = "tsne",min.cutoff = 1,  split.by = "injured_st")
    if(is.na(sub_df[3])){
       p <- p + ggtitle(sub_df[2]) %>% invisible()
    }else{
       p <- p + ggtitle(sub_df[3]) %>% invisible()
    }
    return(p)
}

for(cell_t in unique(selected_genes$cellType)){
    cat("\n")
    cat("###",cell_t," {.tabset} \n")
    df <- selected_genes %>% dplyr::filter(cellType == cell_t)
    df_split <- split(df, ceiling(seq_along(df$geneID)/4))
    for(i in names(df_split)){
        cat("\n")
        cat("####",paste(cell_t,i,sep="-"),"\n")
        
        plot_list <- apply(df_split[[i]],1,FUN = function(x){plot_feature_plot_wrapper(all_data,x)})
        
        
        p_l <- plot_grid(plotlist = plot_list,ncol = 2)
        print(p_l)
        cat("\n")
    }
    cat("\n")
}

```
