---
title: "planC: merge cluster 0, 1, 14, 19 into 0"
author: "Yifang Liu"
date: "`r format(Sys.time(), tz='America/New_York', usetz=TRUE)`"
output:
  rmdformats::html_clean:
    code_folding: hide
    fig_width: 10
    fig_height: 10
    highlight: kate
    thumbnails: false
    lightbox: true
    gallery: true
---

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print = 200)
opts_chunk$set(echo = TRUE,
               cache = FALSE,
               prompt = FALSE,
               tidy = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE)
opts_knit$set(width = 75)
```

```{r setup}
# Specify seed for reproducibility
set.seed(123)

# Setup
library(Matrix)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(Seurat)
library(cowplot)
library(Rcpp)
library(harmony)
```

# Before merge cluster

```{r before_merge}
blood <- readRDS("/Users/m/Projects/Sudhir/Harmony/UNinjured_injured_WASP96hr_res_0.3_0.4_190826/output/blood_190826.Rds")
DefaultAssay(blood) <- "RNA"
resolution <- 0.4
selected_res <- paste0("RNA_snn_res.", resolution)
Idents(blood) <- selected_res
DimPlot(blood, reduction = "tsne", label = TRUE, pt.size = .05)
```

# After merge cluster 0, 1, 14, 19 into 0

```{r after_merge}
# str(blood@meta.data)
merge_cluster <- as.numeric(as.character(blood@meta.data$RNA_snn_res.0.4))
merge_cluster[merge_cluster == 1] <- 0
merge_cluster[merge_cluster == 14] <- 0
merge_cluster[merge_cluster == 19] <- 0
blood@meta.data$merge_cluster <- as.factor(merge_cluster)
# str(blood@meta.data)
# write.table(blood@meta.data, file = "planC_metadata.txt", quote = FALSE, sep = "\t")
selected_res <- "merge_cluster"
Idents(blood) <- selected_res
DimPlot(blood, reduction = "tsne", label = TRUE, pt.size = .05)
saveRDS(blood, file = "output/blood_190912.Rds")
```

```{r findMarkers}
if (file.exists("output/planC_UNinjured_injured_WASP96hr.Rds")) {
  markers_list <- readRDS("output/planC_UNinjured_injured_WASP96hr.Rds")
}else{
  gene_symbol_id <- read.table("/Users/m/Projects/Sudhir/Harmony/UNinjured_injured_WASP96hr_res_0.3_0.4_190826/data/gene_symbol_id_v2.txt", stringsAsFactors = FALSE, row.names = 1)
  table_df <- table(blood@meta.data[ , selected_res], blood@meta.data$Sample) %>%
    as.data.frame() %>% spread(key = Var2, value = Freq)
  colnames(table_df)[1] <- "cluster"
  markers_list <- list()
  for(cluster_id in table_df$cluster){
      markers <- FindMarkers(blood, ident.1 = cluster_id)
      markers$gene_name <- row.names(markers)
      markers$gene_id <- gene_symbol_id[markers$gene_name, ]
      write.csv(markers, file = paste0("output/planC_UNinjured_injured_WASP96hr_", "cluster_", cluster_id, ".csv"))
      markers_list[[paste0("cluster_", cluster_id)]] <- markers
  }
  saveRDS(markers_list,
          file = "output/planC_UNinjured_injured_WASP96hr.Rds")
}
```

## Clusters - t-SNE {.tabset}

```{r plot_marker_genes_clusters_tsne, results = "asis"}
plot_feature_plot_wrapper <- function(obj, sub_df){
  # print(sub_df["gene_name"])
  p <- FeaturePlot(obj, features = sub_df["gene_name"], cols = c("grey", "blue"),
                   reduction = "tsne", pt.size = .05)
  return(p)
}

for(cluster_n in names(markers_list)){
  cat("\n")
  cat("### ", cluster_n, " {.tabset} \n")
  # df <- markers_list[[`cluster_n`]][1:min(12,dim(markers_list[[`cluster_n`]])[1]),]
  df <- markers_list[[`cluster_n`]]
  df <- subset(df, df$avg_logFC > 0)
  df <- df[1:min(20,dim(df)[1]), ]
  df_split <- split(df, ceiling(seq_along(df$gene_name)/4))
  for(i in names(df_split)){
    cat("\n")
    cat("####", paste(cluster_n, i, sep = "-"), "\n")
    plot_list <- apply(df_split[[i]], 1, FUN = function(x){plot_feature_plot_wrapper(blood, x)})
    p_l <- plot_grid(plotlist = plot_list, ncol = 2)
    print(p_l)
    cat("\n")
  }
  cat("\n")
}
```

## Clusters - t-SNE - Split {.tabset}

```{r plot_marker_genes_clusters_tsne_split, results = "asis"}
plot_feature_plot_wrapper <- function(obj, sub_df){
  # print(sub_df["gene_name"])
  p <- FeaturePlot(obj, features = sub_df["gene_name"], cols = c("grey", "blue"),
                   reduction = "tsne", split.by = "Sample", pt.size = .05)
  return(p)
}

for(cluster_n in names(markers_list)){
  cat("\n")
  cat("### ", cluster_n, " {.tabset} \n")
  # df <- markers_list[[`cluster_n`]][1:min(12,dim(markers_list[[`cluster_n`]])[1]),]
  df <- markers_list[[`cluster_n`]]
  df <- subset(df, df$avg_logFC > 0)
  df <- df[1:min(20,dim(df)[1]), ]
  df_split <- split(df, ceiling(seq_along(df$gene_name)/2))
  for(i in names(df_split)){
    cat("\n")
    cat("####", paste(cluster_n, i, sep = "-"), "\n")
    plot_list <- apply(df_split[[i]], 1, FUN = function(x){plot_feature_plot_wrapper(blood, x)})
    p_l <- plot_grid(plotlist = plot_list, ncol = 1)
    print(p_l)
    cat("\n")
  }
  cat("\n")
}
```

## Clusters - Violin {.tabset}

```{r plot_marker_genes_clusters_violin, results = "asis"}
for(cluster_n in names(markers_list)){
  cat("\n")
  cat("### ", cluster_n, " {.tabset} \n")
  df <- markers_list[[`cluster_n`]]
  df <- subset(df, df$avg_logFC > 0)
  df <- df[1:min(20,dim(df)[1]), ]
  df_split <- split(df, ceiling(seq_along(df$gene_name)/1))
  for(i in names(df_split)){
    cat("\n")
    cat("####", paste(cluster_n, i, sep = "-"), "\n")
    plot <- VlnPlot(blood, features = df_split[[i]]$gene_name,group.by = selected_res,
                    pt.size = 0, combine = FALSE)
    p <- plot[[1]] + ggtitle(df_split[[i]]$gene_name)
    print(p)
    cat("\n")
  }
  cat("\n")
}
```

## Clusters - Violin - Split {.tabset}

```{r plot_marker_genes_clusters_violin_split, results = "asis"}
for(cluster_n in names(markers_list)){
  cat("\n")
  cat("### ", cluster_n, " {.tabset} \n")
  df <- markers_list[[`cluster_n`]]
  df <- subset(df, df$avg_logFC > 0)
  df <- df[1:min(20,dim(df)[1]), ]
  df_split <- split(df, ceiling(seq_along(df$gene_name)/1))
  for(i in names(df_split)){
    cat("\n")
    cat("####", paste(cluster_n, i, sep = "-"), "\n")
    plot <- VlnPlot(blood, features = df_split[[i]]$gene_name, group.by = selected_res,
                    pt.size = 0, combine = FALSE, split.by = "Sample")
    p <- plot[[1]] + ggtitle(df_split[[i]]$gene_name)
    print(p)
    cat("\n")
  }
  cat("\n")
}
```

## Clusters - Dotplot - All Cluster {.tabset}

```{r DotPlot_allcluster, results = "asis"}
for (n in c(1:3)) {
  cat("\n")
  cat("### ", paste0("Top ", n, " marker genes in each cluster"), " {.tabset} \n")
  gene_list <- character(length = 0)
  for(cluster_n in names(markers_list)){
    df <- markers_list[[`cluster_n`]]
    df <- subset(df, df$avg_logFC > 0)
    count <- 0
    gene_names <- df$gene_name
    for (i in 1:length(gene_names)) {
      if (gene_names[i] %in% gene_list) {
        # print(cluster_n)
        # print(i)
        # print(gene_names[i])
      } else {
        gene_list <- c(gene_names[i], gene_list)
        count <- count + 1
      }
      if (count == n) {
        break
      }
    }
  }
  p <- DotPlot(blood, features = gene_list,  group.by = selected_res, dot.scale = 7 - n) + RotatedAxis() + ylab("Cluster") + theme(axis.text.x = element_text(size = 11 - n))
  print(p)
  cat("\n")
}
```

## Clusters - Dotplot - Split {.tabset}

```{r DotPlot_split, results = "asis"}
for (n in c(1:3)) {
  cat("\n")
  cat("### ", paste0("Top ", n, " marker genes in each cluster"), " {.tabset} \n")
  gene_list <- character(length = 0)
  for(cluster_n in names(markers_list)){
    df <- markers_list[[`cluster_n`]]
    df <- subset(df, df$avg_logFC > 0)
    count <- 0
    gene_names <- df$gene_name
    for (i in 1:length(gene_names)) {
      if (gene_names[i] %in% gene_list) {
        # print(cluster_n)
        # print(i)
        # print(gene_names[i])
      } else {
        gene_list <- c(gene_names[i], gene_list)
        count <- count + 1
      }
      if (count == n) {
        break
      }
    }
  }
  p <- DotPlot(blood, features = gene_list, group.by = selected_res, dot.scale = 6.3 - n, split.by = "Sample", cols = c("#F25122", "#02A4EF", "#FFBA02")) +
    RotatedAxis() + ylab("Cluster") + theme(axis.text.x = element_text(size = 10 - n))
  print(p)
  cat("\n")
}
```

## Clusters - Heatmap {.tabset}

```{r clusters_heatmap, results = "asis"}
for (n in c(3, 5, 10)) {
  cat("\n")
  cat("### ", paste0("Top ", n," marker genes in each cluster"), " {.tabset} \n")
  gene_list <- c()
  for(cluster_n in names(markers_list)){
    df <- markers_list[[`cluster_n`]]
    df <- subset(df, df$avg_logFC > 0)
    df <- df[1:min(n, dim(df)[1]), ]
    gene_list <- c(gene_list, df$gene_name)
  }
  # gene_list <- gene_list %>% rev() %>% unique() %>% rev()
  p <- DoHeatmap(blood, features = gene_list)
  print(p)
  cat("\n")
}
```

## Clusters - Heatmap - Downsample300 {.tabset}

Downsample the clusters to a maximum of 300 cells each (makes the heatmap easier to see for small clusters)

```{r clusters_heatmap_Downsample300, results = "asis"}
for (n in c(3, 5, 10)) {
  cat("\n")
  cat("### ", paste0("Top ", n, " marker genes in each cluster"), " {.tabset} \n")
  gene_list <- c()
  for(cluster_n in names(markers_list)){
    df <- markers_list[[`cluster_n`]]
    df <- subset(df, df$avg_logFC > 0)
    df <- df[1:min(n, dim(df)[1]), ]
    gene_list <- c(gene_list, df$gene_name)
  }
  # gene_list <- gene_list %>% rev() %>% unique() %>% rev()
  p <- DoHeatmap(subset(blood, downsample = 300), features = gene_list)
  print(p)
  cat("\n")
}
```

# Notes

Wed Sep 11, 2019:

  * planC: merge cluster 0, 1, 14, 19 into 0.

Tuesday, August 27, 2019:

  * If a marker is already appeared in previous cluster, the follow up marker will be added, so that every cluster will have the same number of markers.

Monday, August 26, 2019:

  * Add marker genes, dotplot, heatmap.

Sunday, August 25, 2019:

  * If a gene express two out of three samples, we will keep these genes.

Friday, August 9, 2019:

  * Integrate analysis of UNinjured, injured and WASP96hr data, add Markers combined map.

Friday, August 2, 2019:

  * Split sample to different libraries, add QC, add combined map, change resolution (0.1 to 1).

Thursday, August 1, 2019:

  * Select the list of all cells of the 2 clusters (cluster 6 and 10) and do a clustering to see the sub-clusters.

Monday, July 29, 2019:

  * First version for integrate analysis of UNinjured injured WASP 10x indrop dropseq data.

# Session Info
```{r sessioninfo, message=TRUE}
sessionInfo()
```

